---
title: "Available Data Show"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)
library(sf)
library(here)
library(ggthemes)
library(raster)
```

```{r, include = FALSE}

### read in shapefiles ###

## Administrative boundaries
soco_bound <- read_sf(here("data/clean/sonoma_county_boundary/sonoma_county_boundary.shp"))
ca_state <- sf::read_sf(here("data/clean/ca_state_boundary/ca_state_boundary.shp"))

## Hazards
flood_awareness <- read_sf(here("data/clean/flood_awareness_areas/flood_awareness_areas.shp"))
landslide_risk <- raster(here("data/clean/soco_landslide_risk/ls_risk.tif"))
bcm_data <- read_sf(here("data/clean/soco_bcm/soco_bcm_full_ws.shp"))
fire_risk <- read_sf(here("data/clean/soco_wildfire_risk_index/Wildfire_Risk_Index.shp"))
slr_75cm <- read_sf(here("data/clean/fldhazd_slr75_w000/all_fldhazd_slr75_w000.shp"))
slr_75cm_100yr <- read_sf(here("data/clean/fldhazd_slr75_w100/all_fldhazd_slr75_w100.shp"))
slr_200cm <- read_sf(here("data/clean/fldhazd_slr200_w000/all_fldhazd_slr200_w000.shp"))

## Comunity assets
priority_pops <- read_sf(here("data/clean/soco_priority_pops_ces3_2021/soco_priority_pop.shp"))
calenviro <- read_sf(here("data/clean/soco_calenviroscreen_4.0/soco_calenviro.shp"))
```

#### **Data source:** []()

## **Hazards**

### Sea Level Rise

#### **Data source:** [Our Coast Our Future](https://ourcoastourfuture.org/hazard-map/)

```{r, echo = FALSE}
ggplot() +
  geom_sf(data = ca_state, fill = "grey") +
  geom_sf(data = soco_bound, fill = "lightgrey") +
  geom_sf(data = slr_200cm, fill = "#011f4b", color = "#011f4b") +
  geom_sf(data = slr_75cm_100yr, fill = "#005b96", color = "#005b96") +
  geom_sf(data = slr_75cm, fill = "#6497b1", color = "#6497b1") +
  geom_sf(data = soco_bound, fill = NA) +
  labs(
    title = "200 cm (6.6 ft) [dark blue] / 75 cm (2.5 ft) + 100 yr flood [medium blue]/ 75 cm (2.5 ft)  [light blue]"
  ) +
  coord_sf(xlim = c(-123.5,-122.3), ylim = c(38.15,38.85)) +
  theme_map()
    
```


### Floodplains

#### **Data source:** [Vital Lands](https://sonomaopenspace.egnyte.com/fl/Io8VY7hySY#folder-link/Flood_Awareness_Areas)

```{r, echo = FALSE}
# flood zones
floodplains <- flood_awareness %>% 
  filter(CLASS %in% c("Russian River Floodplain", "Mark West Creek Floodplain", "Floodplain"))

ggplot() +
  geom_sf(data = soco_bound, fill = "lightgrey") +
  geom_sf(data = floodplains, fill = "blue", color = "blue") +
  theme_map()
```

### Landslide risk

#### **Data source:** [California Geological Survey](https://gis.conservation.ca.gov/portal/home/item.html?id=87289025c11d4ba7ae65f0f472bf7c2d) 

```{r, echo = FALSE}
plot(landslide_risk)
```

### Sonoma County Wildfire Hazard Index

#### **Data source:** [Sonoma County](https://storymaps.arcgis.com/stories/a64d596a8be941c8b28263718880e433)

```{r, echo = FALSE}

ggplot() +
  geom_sf(data = fire_risk, aes(fill = HEX_TUKMAN), color = NA) +
  scale_fill_distiller(palette = "YlOrRd", direction = 1) +
  geom_sf(data = soco_bound, color = "black", fill = NA) +
  labs(
    title = "",
    fill = "Rank"
  ) +
  theme_map() +
  theme(legend.position = "right")

```


### Sonoma County Wildfire Risk Index

#### **Data source:** [Sonoma County CWPP Hub Site](https://sonoma-county-cwpp-hub-site-sonomacounty.hub.arcgis.com/datasets/wildfire-risk-index/explore?location=38.480883%2C-122.941170%2C10.41)

```{r, echo = FALSE}

ggplot() +
  geom_sf(data = fire_risk, aes(fill = TOTAL_RANK), color = NA) +
  scale_fill_distiller(palette = "YlOrRd", direction = 1) +
  geom_sf(data = soco_bound, color = "black", fill = NA) +
  labs(
    title = "",
    fill = "Rank"
  ) +
  theme_map() +
  theme(legend.position = "right")

```


### BCM data

#### **Data source:** [San Francisco Bay Area Climate-Smart Watershed Analyst](http://climate.calcommons.org/tbc3/sf-bay-watershed-analyst)

```{r, echo = FALSE, fig.width=10, fig.height=4}

bcm_ccsm <- bcm_data %>% 
  filter(gcm == "CCSM4_rcp85") 

source(here("R/utils/bcm_plot.R"))

# CWD
bcm_plot(bcm_ccsm$cwd, "Climatic Water Deficit", "YlOrRd")

# Ppt
bcm_plot(bcm_ccsm$ppt, "Precipitation", "YlGnBu")

# tmax
bcm_plot(bcm_ccsm$tmax, "Max Temperature", "YlOrBr")

# tmin
bcm_plot(bcm_ccsm$tmin, "Min Temperature", "Blues", pal_dir = -1)

```



```{r, echo = FALSE}
### Projected fire probability

#### **Data source:** [Park et al. (2021)](https://datadryad.org/stash/dataset/doi:10.25349/D96W4W)
```


## **Community Assets**

### Priority populations

#### **Data source:** [California Climate Investments Priority Populations 3.0 by Census Tract](https://webmaps.arb.ca.gov/PriorityPopulations/)

```{r, echo = FALSE, fig.width=10, fig.height=4}

ggplot() +
  geom_sf(data = soco_bound) +
  geom_sf(data = priority_pops, aes(fill = category)) +
  theme_map() +
  theme(legend.position = "right")

```

### CalEnviroScreen

#### **Data source:** [CalEnviroScreen 4.0](https://oehha.ca.gov/calenviroscreen/report/calenviroscreen-40)

```{r, echo = FALSE}

# housing buredened
ggplot() +
  geom_sf(data = calenviro, aes(fill = HousBurd)) +
  scale_fill_distiller(palette = "Blues", direction = 1) +
  labs(
    title = "Percent housing-burdened low-income households",
    fill = "Percent"
  ) +
  theme_map() +
  theme(legend.position = "right")

# Poverty
ggplot() +
  geom_sf(data = calenviro, aes(fill = Poverty)) +
  scale_fill_distiller(palette = "Oranges", direction = 1) +
  labs(
    title = "Percent of population living below two times the federal poverty level",
    fill = "Percent"
  ) +
  theme_map() +
  theme(legend.position = "right")

# Elderly over 65
ggplot() +
  geom_sf(data = calenviro, aes(fill = Elderly65)) +
  scale_fill_distiller(palette = "Purples", direction = 1) +
  labs(
    title = "2019 ACS population estimates of the percent per census tract of elderly 65 years and older",
    fill = "Percent"
  ) +
  theme_map() +
  theme(legend.position = "right")



```

